Assessing Gender Bias in Machine Translation

### 2017-12-16 paper/main.tex
Wrapping up

With this in mind, we propose a quantitative analysis of the phenomenon of gender bias in machine translation. We believe this can be done by simply exploiting Google Translate to map sentences from a gender neutral language to English, as Figure \ref{fig:screenshot-gtranslate-hungarian} exemplifies.

>>>>

With this in mind, we propose a quantitative analysis of the phenomenon of gender bias in machine translation. We believe this can be done by simply exploiting Google Translate to map sentences from a gender neutral language to English. As Figure \ref{fig:screenshot-gtranslate-hungarian} exemplifies, this approach
